\chapter{Acknowledgements}
I would like to thank my supervisor for this MSc project, Jeppe Revall Frisvad, for the constant support and help during the whole duration of this thesis. His constant help and meetings in his office, as well as his prompt replies to my e-mails, have been determinant in the development of this thesis. I would also like to thank professor Neils J\o rgen Christiansen for his suggestions and support during the weekly group meetings.

A special acknowledgment should be given to the T.I.M.E. double degree program, for giving me the opportunity to fulfill my dream of completing a Master Degree abroad. Without them, all my achievements in the past two years would not have been possible. From the University of Padua, I would like to thank professor Maria Elena Valcher, for helping with my study plan and all the bureaucracy a double degree program requires, and professor Emanuele Menegatti, for accepting on being my advisor for my MSc defense in Italy.

Finally, on a personal note, I would like to thank my family for the constant support they give to me, supporting also in my decision to study abroad. Of my friends, a special thank you is owed to my italo-colombian friend Marco Fraccaro for the help and the support in the last two years. I would also like to personally thank my colleague and Giacomo Baruzzo for in reading my thesis and giving suggestions on it. It is really impossible to list all the people that morally supported me during this master thesis, but I would like to thank them all for cheering me up during the most difficult moments of this thesis.    